\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Final Project EDT}
\author{Santiago Chitiva \\ Valeria Caycedo \\ Samuel Campos \\ Erick Salazar \\ Juan E. Díaz}
\date{May 2026}

\begin{document}

\maketitle

\section{Phase 1: Problem Definition and Data Acquisition}

\subsection{Event Definition and Study Area}

This project revisits the case study analyzed in the Midterm Project: the collapse
of the Kakhovka Dam on June 6, 2023, located on the Dnieper River in Kherson Oblast,
southern Ukraine. The event caused catastrophic downstream flooding and the rapid
drainage of the Kakhovka Reservoir, making it one of the most significant
hydrological disasters in recent European history.

The Region of Interest (ROI) is centered on the area surrounding Nova Kakhovka,
where the effects of reservoir drainage were most clearly observable in satellite
imagery. This ROI was selected based on image availability and the visibility of
hydrological changes between the pre- and post-event dates.

\subsection{Satellite Imagery Metadata}

Two Sentinel-2 Level-2A images were acquired from the Copernicus Open Access Hub.
Table~\ref{tab:imagery_metadata} summarizes their main technical characteristics.

\begin{table}[h]
    \centering
    \caption{Technical characteristics of the satellite imagery used.}
    \label{tab:imagery_metadata}
    \begin{tabular}{lllllll}
        \hline
        \textbf{Date} & \textbf{Satellite} & \textbf{Level} &
        \textbf{Resolution} & \textbf{Cloud Cover} & \textbf{Role} \\
        \hline
        June 18, 2023 & Sentinel-2 A/B & Level-2A & 10 m & $<$30\% & Post-event \\
        \hline
    \end{tabular}
\end{table}

Level-2A products provide Bottom-of-Atmosphere (BOA) reflectance, eliminating the
need for additional atmospheric correction. The bands used for this project span
from the visible to the shortwave infrared spectrum, as detailed in
Table~\ref{tab:bands}.

\begin{table}[h]
    \centering
    \caption{Sentinel-2 spectral bands used for dataset construction.}
    \label{tab:bands}
    \begin{tabular}{cll}
        \hline
        \textbf{Band} & \textbf{Name} & \textbf{Wavelength ($\mu$m)} \\
        \hline
        B2  & Blue                   & 0.490 \\
        B3  & Green                  & 0.560 \\
        B4  & Red                    & 0.665 \\
        B5  & Red Edge 1             & 0.705 \\
        B6  & Red Edge 2             & 0.740 \\
        B7  & Red Edge 3             & 0.783 \\
        B8  & Near-Infrared (NIR)    & 0.842 \\
        B8A & Narrow NIR             & 0.865 \\
        B11 & SWIR 1                 & 1.610 \\
        B12 & SWIR 2                 & 2.190 \\
        \hline
    \end{tabular}
\end{table}

\subsection{Dataset Construction}

To prepare the training dataset for the machine learning phase, pixel values were
extracted from the Sentinel-2 band stack at the locations defined by the training
polygons digitized in QGIS. Each polygon corresponds to one of four land cover
classes: Water, Vegetation, Bare Soil, and Built-up.

The extraction was performed using a Python script based on the \texttt{rasterio}
and \texttt{geopandas} libraries. For each pixel falling within a training polygon,
the script records its geographic coordinates (Latitude, Longitude), the reflectance
values for all ten spectral bands, and the corresponding class label. The output was
exported as a Tab-Separated Values (TSV) file, as required for the subsequent
training phase.

Table~\ref{tab:tsv_structure} illustrates the structure of the resulting dataset.

\begin{table}[h]
    \centering
    \caption{Structure of the exported TSV training dataset.}
    \label{tab:tsv_structure}
    \begin{tabular}{lll}
        \hline
        \textbf{Column} & \textbf{Type} & \textbf{Description} \\
        \hline
        Latitude  & Float  & Geographic latitude of the pixel centroid \\
        Longitude & Float  & Geographic longitude of the pixel centroid \\
        B2        & Float  & Blue band reflectance \\
        B3        & Float  & Green band reflectance \\
        B4        & Float  & Red band reflectance \\
        B5        & Float  & Red Edge 1 reflectance \\
        B6        & Float  & Red Edge 2 reflectance \\
        B7        & Float  & Red Edge 3 reflectance \\
        B8        & Float  & NIR band reflectance \\
        B8A       & Float  & Narrow NIR reflectance \\
        B11       & Float  & SWIR 1 reflectance \\
        B12       & Float  & SWIR 2 reflectance \\
        label     & String & Land cover class (Water, Vegetation, Bare Soil, Built-up) \\
        \hline
    \end{tabular}
\end{table}

\section{Phase 2: Pre-processing and Training}

\subsection{Pre-procesing}

\subsection{Models}

\subsubsection{Decision Trees (DT)}

\subsubsection{Support Vector Machine (SVM)}

\subsubsection{Artificial Neural Networks (ANN)}

\subsubsection{K-Nearest Neighbor (KNN)}

\subsubsection{Naive Bayes (NB)}

\section{Phase 3: Synthesis and Prediction}

\end{document}
